---
title: "Birth seasonality - Figures"
author: "Laura Symul - Micaela Martinez"
date: "last update: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2: 
    theme: cosmo
    highlight: haddock
    toc: yes
    toc_float: true
    toc_depth: 5
    number_sections: true
    fig_caption: true
---

```{r 10-figs-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```


```{r 10-figs-project-setup, include=FALSE, cache = FALSE}
source("Scripts/00_setup.R")
```

# Main and Supplementary Figures


## Figure 1: Datasets (births data and sex data)

### Births data

```{r 10-load-birth-data}

official_birth_records = 
  read_feather(
    path = 
      str_c("../Data/5_outputs/official_birth_records.feather")
  )

```

```{r 10-plot-births-data, fig.height=6, fig.width=6}

official_birth_records = official_birth_records %>% 
  mutate(births_thousands = births/1000)

official_births_summary = official_birth_records %>% 
  group_by(country_area, country_area_col) %>% 
  summarize(min_births = min(births_thousands),
            max_births = max(births_thousands),
            mean_births = mean(births_thousands),
            max_date = max(date))

ref_date = as.Date("2020-01-01")

g_births = ggplot(official_birth_records, 
                  aes(x = date, y = births_thousands,
                      col = country_area_col))

g_births = g_births +
  #### reference for variations
  geom_segment(data = official_births_summary, 
               aes(x = ref_date, xend = ref_date, 
                   y = mean_births, yend = mean_births-5*mean_births/100),
               size = 1.5, alpha = 0.7)+
  # geom_text(data = official_births_summary, aes(x = ref_date, y = min_births-5*mean_births/100), label = "5% change from the mean",
  #           hjust = 0, vjust = 0, nudge_x = 100)+
  #### uncorrected births
  geom_line(aes(y = births_original_numbers/1000), col = "gray80")+
  #### corrected births
  geom_line()+   #geom_point(size = 0.5)+
  #### COUNTRIES
  geom_text(data = official_births_summary, 
            aes(x = ref_date, y = max_births *1.05, 
                label = country_area, fontface = 2), 
            vjust = 0, hjust = 1)+
  #### settings
  scale_color_identity()+
  scale_x_date(date_minor_breaks = "1 year", date_labels = "%Y")+
  scale_y_continuous(expand = expansion(mult = c(0,0.2)))+ 
  # sec.axis = sec_axis(~ (. - max(.))/max(.)*100, breaks = seq(-30,30,by = 10), name = "% change from the max") 
  ylab("Births (monthly in thousands)") + 
  xlab("Date")+
  facet_grid(country_area ~., scale = "free") +
  theme(strip.text.y = element_blank())

# g_births

```


### App data (sexual activity data)

```{r 10-overal-sex-data-for-all-locations-together}

pp = read_feather(path = "../Data/4_clue_data_aggregated/aggregated_sex_counts_clue_July2017-June2019_incl.feather")

pp_sum = pp %>%
  filter(BC == "all", age_cat == "all") %>% 
  mutate(sex_type_str = 
           case_when(
             sex_type == "all_sex" ~ "Total Sex", 
             sex_type == "prot_sex" ~ "Protected Sex",
             sex_type == "unprot_sex" ~ "Unprotected Sex")) %>% 
  group_by(date, sex_type, sex_type_str) %>% 
  summarize(n_users = sum(n_users),
            n_any  = sum(n_any),
            n_log = sum(n),
            .groups = "drop") %>% 
  group_by(sex_type) %>% 
  mutate(relative_frequency = n_log / n_any,
         relative_frequency = relative_frequency/mean(relative_frequency)) %>% 
  arrange(sex_type , date) %>% ungroup() %>%  
  mutate(
    sex_type_str = sex_type_str %>% 
      factor(., levels = c("Total Sex","Protected Sex","Unprotected Sex"))
    )

sex_colors = c("gray40","steelblue2","yellow3")

g_sex_freq = 
  ggplot(pp_sum, 
         aes(x = date, y = relative_frequency, 
             col = sex_type_str))+
  geom_line()+
  ylab("Relative sex frequency (daily)")+xlab("Date")+
  #expand_limits(y = 0)+  
  scale_color_manual(name = "", values = sex_colors)+
  facet_grid(sex_type_str ~ .)+
  guides(col = FALSE) +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.title = element_blank(),
        legend.background = 
          element_rect(fill = "white", 
                       color = "transparent", 
                       size = 0.5)) 

# g_sex_freq

```


### Clue tracking screen

```{r 10-clue-tracking-screen}

# import png
clue_screen = image_read("../Figures Tables Media/Media/Clue_app_screens.png")

clue_screen_ratio = image_info(clue_screen)$height / image_info(clue_screen)$width 
padding = 20
g_clue_screen = ggplot()+ coord_fixed(ratio = clue_screen_ratio)+
  background_image(clue_screen)+theme(plot.margin = margin(t=padding, l=padding, r=padding, b=padding, unit = "pt"))

```


### Assembled Figure 1 


```{r 10-fig1, fig.width=10, fig.height=7, cache = FALSE}


fig_1 = arrangeGrob(
  g_births,     
  g_clue_screen,   
  g_sex_freq,
  ncol = 2, nrow = 2, 
  widths = c(1.5, 1),
  heights = c(0.55,0.45),
  layout_matrix = cbind(c(1,1), c(3,4)))

fig_1 = as_ggplot(fig_1) + 
  draw_plot_label(label = letters[1:3], size = 15,
                  x = c(0, 0.6, 0.6), y = c(1, 1, 0.45))

# fig_1


```


## Supplementary Figure 1: Sex data for each location separately


```{r 10-suppl-fig-1, fig.width=7, fig.height=9}

pp = pp %>% 
  mutate(Sex_type = 
           sex_type %>% 
           str_replace(.,"_","\n") %>% 
           str_replace(., "prot", "protected") %>% 
           str_to_sentence())

suppl_fig_1_plotlist = 
  map(
    .x = unique(pp$country_area) %>% sort(),
    .f = function(loc){
      
      this_loc_sex = 
        pp %>% filter(country_area == loc)
      
      this_loc_holidays = 
        get_holidays(
          countries = loc %>% str_split_fixed(.," - ",2) %>% first(),
          year_range = c(2017,2019),
          hdict = dict$holidays) %>% 
        filter(date %in% this_loc_sex$date)
      
      ggplot(this_loc_sex, 
             aes(x = date)) +
        geom_point(
          data = this_loc_holidays,
          aes(y = min(this_loc_sex$x)-0.05),
          shape = 17, col = "gray"
        ) +
        geom_line(aes(y = x, col = sex_type)) +
        guides(col = FALSE) +
        scale_color_manual(values = sex_colors) + 
        facet_grid(Sex_type ~ ., scale = "free_y") +
        ggtitle(loc) +
        xlab("Date") +
        ylab("Relative sexual frequency")

    }
  )
  
  
suppl_fig_1 = 
  ggarrange(plotlist = suppl_fig_1_plotlist,
            ncol = 2, nrow = 3, 
            labels = "auto")

# suppl_fig_1

```


## Figure 2 and Suppl. Figure 2: Sexual activity model coefficients

```{r 10-load-sex-models}

# load Figure 2 data

load(file = str_c(IO$p_outputs,"sex_models_df.Rdata"), verbose = TRUE)

```


```{r 10-plot-sex-model-coef}

plotlist = list()
n_items = c()
cas = unique(sex_models_df$country_area)
ok = foreach(ca = cas) %do% {
  cat(ca, "\n")
  
  # retrieving the model for this country and only plotting for BC all and sex_type all
  load(
    file = str_c(
      "../Data/5_outputs/sex_models/",
      "sex_model_",ca,
      "_BC_all_age_cat_all_sex_type_all_sex.Rdata"
    ),
    verbose = TRUE
  )
  glm_sex_behavior = this_sex_model$model
  
  # Visualisation of the coefficient
  g_coef = ggplot_sex_activity_glm_coefficient(
    model = glm_sex_behavior, 
    show_intercept = FALSE, 
    show_weekly_patterns = FALSE, 
    ylim = c(-0.4, 1))
  g_coef = g_coef + 
    ggtitle(ca)+
    theme(axis.text.x = element_text(size = 7))
  # print(g_coef)
  
  plotlist[[ca]] = g_coef
  n_items = c(n_items, nrow(g_coef$data))
}

```


```{r 10-assembled-figure-2, fig.width = 14, fig.height=7, cache = FALSE}

fig_2 = ggarrange(
  ggarrange(
    plotlist[[which(cas == "Brazil - Central-West")]], 
    plotlist[[which(cas == "United States - Northeast")]], 
    labels = c("a","b"),
    ncol = 2, nrow = 1,
    widths = n_items[which(cas %in% c("Brazil - Central-West","United States - Northeast"))] / 
      sum(n_items[which(cas %in% c("Brazil - Central-West","United States - Northeast"))])
  ),
  ggarrange(
    plotlist[[which(cas == "France")]], 
    plotlist[[which(cas == "United Kingdom")]], 
    labels = c("c","d"),
    ncol = 2, nrow = 1,
    widths = n_items[which(cas %in% c("France","United Kingdom"))] / 
      sum(n_items[which(cas %in% c("France","United Kingdom"))])
  ),
  nrow = 2, ncol = 1
)

# fig_2

```



```{r 10-suppl-fig-2, fig.height = 10, fig.width = 8}

suppl_fig_2 = 
  ggarrange(
    plotlist = plotlist,
    nrow = 3, ncol = 2,
    labels = "auto"
)

# suppl_fig_2

```



## Figure 3, Suppl. Figures 3, 4 and 5: Mathematical models, seasonal fertility and simulated births

### Model schematics

```{r 10-load-models-schematics-images, cache = FALSE}

model = image_read("../Figures Tables Media/Media/Figure 3-01.png")
model_ratio =  image_info(model)$height / image_info(model)$width 
g_model = ggplot()+ coord_fixed(ratio = model_ratio)+
  background_image(model)



models = image_read("../Figures Tables Media/Media/Figure 3-04.png")
models_ratio = image_info(models)$height / image_info(models)$width
g_models = ggplot()+ coord_fixed(ratio = models_ratio)+
  background_image(models)


```


### Seasonal trends

```{r 10-seasonal-trends}

# model_colors = c("turquoise3","sienna3","maroon3")

model_colors = c(
  hsv(h = 41.45/360, s = 1, v = 0.98),
  hsv(h = 188/360, s = 1, v = 0.7882),
  hsv(h = 17.94/360, s = 0.8392, v = 1)  
)


ca_levels = dict$country_area$country_area


# we load the seasonal trend data
births_STL = read_feather(path = str_c(IO$p_outputs, "simulated_births_seasonal_trends.feather"))
births_STL = births_STL %>% mutate(country_area = factor(country_area, levels = ca_levels))


# we also load the AIC values
opt_par_df = read_feather(path = str_c(IO$p_outputs, "optimal_parameters_and_AIC.feather"))
opt_par_df = opt_par_df %>% mutate(country_area = factor(country_area, levels = ca_levels))
AIC = 
  opt_par_df %>% 
  filter(age_cat == "all",
         BC == "all",
         sex_type == "unprot_sex") %>% 
  select(country_area, model, AIC)


# we create one ggplot object per country

g_st_list = map(
  .x = ca_levels,
  .f = function(ca){
    
    this_ca_births_STL = 
      births_STL %>% 
      filter(country_area == ca)
    
    yaxis_lim = 
      c(this_ca_births_STL$births_seasonal,
        this_ca_births_STL$sim_births_seasonal) %>% 
      range() %>% abs() %>% min() %>% 
      divide_by(1000) %>% round()
    yaxis = c(-yaxis_lim, 0, yaxis_lim)
    
    yaxis_limits = 
      c(this_ca_births_STL$births_seasonal,
        this_ca_births_STL$sim_births_seasonal) %>% 
      range() %>% abs() %>% max() %>% 
      multiply_by(c(-1.04,1.04)) %>% divide_by(1000)
      
    
    g = ggplot(this_ca_births_STL, aes(x = month))
    g + 
      geom_text(
        data = AIC %>% filter(country_area == ca),
        aes(x = ifelse(str_detect(ca, "Brazil"),1.5, 12),
            y = -Inf,
            hjust = ifelse(str_detect(ca, "Brazil"),0, 1),
            vjust = 0,
            label = str_c(model, " : ",AIC %>% round()),
            col = model),
        size = 3
      ) +
      geom_hline(yintercept = 0, col = "gray80") +
      geom_line(aes(y = births_seasonal/1000), col = "black", size = 1) +
      geom_line(aes(y = sim_births_seasonal/1000, col = model),) +
      scale_x_continuous(breaks = seq(0,12,by = 3), minor_breaks = 0:12) +
      scale_y_continuous(breaks = yaxis, minor_breaks = -10:10, limits = yaxis_limits) +
      scale_color_manual(values = model_colors) +
      guides(col = FALSE)+
      xlab(ifelse(ca == ca_levels[3],"Calendar months","")) + 
      ylab(ifelse(ca == ca_levels[1],"Seasonal trends [births, thousands]","")) +
      facet_grid(model ~ .) +
      ggtitle(ca %>% 
                str_replace(.," - ","\n") %>% 
                str_replace(., "United States", "US") %>% 
                str_replace(., "United Kingdom", "UK")) +
      theme(strip.text.y = element_blank(),
            plot.title  = element_text(hjust = 0.5, size = 10))
  }
)

g_st = ggarrange(plotlist = g_st_list, ncol = 6, nrow = 1, align = "h")

# g_st

```

### Time-series

```{r 10-model-C-time-series}

births = read_feather(path = str_c(IO$p_outputs, "simulated_births.feather"))

g_b_list = 
  map(
    .x = ca_levels[c(1,4,2,3,5,6)],
    .f = function(ca){
      g = ggplot(births %>% 
                   filter(country_area == ca,
                          model == "C",
                          age_cat == "all",
                          sex_type == "unprot_sex",
                          BC == "all"),
                 aes(x = year_month))
      g +
        geom_line(aes(y = births/1000), size = 1, col = "black") +
        geom_line(aes(y = sim_births/1000), col = model_colors[3]) +
        ylab(ifelse(ca == "Brazil - Northeast", "Births (thousands)","")) +
        xlab(ifelse(ca %in% c("France","United Kingdom"),"Date","")) +
        ggtitle(ca) +
        theme(plot.title = element_text(size = 10))
    }
  )


g_b = ggarrange(plotlist = g_b_list, ncol = 2, nrow = 3, align = "hv")

# g_b

```


```{r 10-all-models-time-series}


g_all_mod_b_list = 
  map(
    .x = ca_levels,
    .f = function(ca){
      g = ggplot(births %>% 
                   filter(country_area == ca,
                          age_cat == "all",
                          sex_type == "unprot_sex",
                          BC == "all"),
                 aes(x = year_month))
      g +
        geom_line(aes(y = births/1000), size = 1, col = "black") +
        geom_line(aes(y = sim_births/1000, col = model)) +
        scale_color_manual(values = model_colors, guide = "none") +
        ylab(ifelse(ca == "Brazil - Northeast", "Births (thousands)","")) +
        xlab(ifelse(ca %in% c("France","United Kingdom"),"Date","")) +
        ggtitle(ca) +
        facet_grid(model ~ ., labeller = label_both) + 
        theme(plot.title = element_text(size = 10))
    }
  )


suppl_fig_3 = ggarrange(plotlist = g_all_mod_b_list, ncol = 2, nrow = 3, align = "hv", labels = "auto")

# suppl_fig_3

```



### Fertility phase and amplitude


```{r 10-fertility-phase-and-amplitude-polar-plots}

ca_wrapped_levels = dict$country_area$country_area %>% str_replace(.," - ","\n")

opt_par_df = read_feather(path = str_c(IO$p_outputs, "optimal_parameters_and_AIC.feather"))
opt_par_df =
  opt_par_df %>% 
  mutate(
    country_area = factor(country_area, levels = ca_levels),
    country_area_wrapped = str_replace(country_area," - ","\n") %>%  
      factor(., levels = ca_wrapped_levels),
    Amplitude = 100*alpha
  )


DF = opt_par_df %>% 
  filter(model != "A", 
         sex_type == "unprot_sex", 
         BC == "all",
         age_cat == "all")

g_F = ggplot(DF, aes(x = Tp, y = Amplitude, col = country_area_col))
g_F = g_F +
  geom_segment(aes(xend = Tp, yend = 0, linetype = model))+
  geom_point()+
  scale_color_identity(guide = "legend",
                       labels = ca_wrapped_levels, 
                       name = "location" )+
  scale_x_continuous(limits = c(0,1),breaks = seq(0,3/4,by = 1/4), labels = c("Jan","Apr","Jul","Oct"))+
  ylab("Amplitude (% from mean)")+ xlab("Fertility peak time")+
  coord_polar(theta = "x", start = 0)+
  ggtitle("Calendar year")
# g_F


DF = DF %>%
  mutate(
    country = str_split_fixed(country_area, " - ",2)[,1],
    Tp_seas = (Tp-10/365 - 0.5*(country == "Brazil"))%%1)

g_F_seas = ggplot(DF, 
                  aes(x = Tp_seas, 
                      y = Amplitude, 
                      col = country_area_wrapped))
g_F_seas = g_F_seas +
  geom_segment(aes(xend = Tp_seas, yend = 0, linetype = model))+
  geom_point()+
  scale_color_manual(values = dict$country_area$country_area_col, 
                      name = "location" )+
  scale_y_continuous(position = "left", breaks = seq(2, 6, by = 2))+
  scale_x_continuous(limits = c(0,1), breaks = seq(0,3/4,by = 1/4), 
                     labels = c("Winter\nSolstice",
                                "Spring\nEquinox",
                                "Summer\nSolstice",
                                "Autumn\nEquinox")) +
  ylab("Amplitude (% of mean)") + xlab("Fertility peak time") +
  coord_polar(theta = "x", start = 0, clip = "off") +
  ggtitle("Solar year") +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom",
    legend.direction = "vertical",
    legend.key.height = unit(22,"pt")
  )
# g_F_seas


```


```{r 10-fertility-sine-curves}


df_sine_curves = expand.grid(t = seq(0,12,by = 0.1), country_area = DF$country_area)
df_sine_curves = left_join(df_sine_curves, 
                           DF %>% 
                             filter(sex_type == "unprot_sex", BC == "all", model == "C") %>% 
                             select(country_area, country_area_col, country_area_wrapped,  alpha, Amplitude, Tp, Tp_seas) %>% 
                             ungroup(),
                           by = "country_area")

df_sine_curves = df_sine_curves %>% 
  mutate(
    Fertility_calendar = 100 + Amplitude * cos(t/12*2*pi - Tp*2*pi),
    Fertility_solar = 100 + Amplitude * cos(t/12*2*pi - Tp_seas*2*pi)
  )


g_fert = ggplot(df_sine_curves, aes(x = t, y = Fertility_calendar, col = country_area_col))+
  geom_hline(yintercept = 100, col = "gray75")+
  geom_line(size = 0.8)+
  scale_color_identity()+
  scale_x_continuous(breaks = seq(0,12,by = 3), minor_breaks = 0:12, labels = c("Jan","Apr","Jul","Oct","Jan"))+
  xlab("Calendar months")+
  ylab("Relative changes in fertility (%)")
# g_fert

g_fert_solar = ggplot(df_sine_curves, aes(x = t, y = Fertility_solar, col = country_area_col))+
  geom_hline(yintercept = 100, col = "gray75")+
  geom_line(size = 0.8)+
  scale_color_identity()+
  scale_x_continuous(breaks = seq(0,12,by = 3), minor_breaks = 0:12, 
                     labels = c("Winter\nSolstice","Spring\nEquinox","Summer\nSolstice","Autumn\nEquinox","Winter\nSolstice"))+
  xlab("Solar time")+
  ylab("Relative changes in fertility (%)")
# g_fert_solar

```

### Amplitude comparison in model C (sex vs fertility)

```{r 10-amplitude-comparison}

suppl_fig_4_list = 
  map(
    .x = unique(births_STL$country_area),
    .f = function(loc){
      
      opt_par_model_C = 
        opt_par_df %>% 
        filter(country_area == loc,
               model == "C",
               sex_type == "unprot_sex",
               age_cat == "all",
               BC == "all")
      
      opt_par_model_B = 
        opt_par_df %>% 
        filter(country_area == loc,
               model == "B",
               sex_type == "unprot_sex",
               age_cat == "all",
               BC == "all")
      
      
      
      seas_trend = 
        births_STL %>% 
        filter(country_area == loc,
               sex_type == "unprot_sex",
               age_cat == "all",
               BC == "all") %>% 
        group_by(model, month) %>% 
        slice_head(n = 1) %>%  ungroup()
      
      coef_A = opt_par_model_C$beta
      ratio_B = opt_par_model_C$alpha/opt_par_model_B$alpha
      
      amplitudes_df = 
        bind_rows(
          seas_trend %>% 
            filter(model == "A") %>% 
            select(month, sim_births_seasonal)  %>% 
            rename(value = sim_births_seasonal) %>% 
            mutate(value = value * coef_A,
                   variable  = "Sex",
                   group = "A"),
          seas_trend %>% 
            filter(model == "B") %>% 
            select(month, sim_births_seasonal)  %>% 
            rename(value = sim_births_seasonal) %>% 
            mutate(value = value * ratio_B,
                   variable  = "Fertility",
                   group = "A"),
          seas_trend %>% 
            filter(model == "C") %>% 
            select(month, sim_births_seasonal)  %>% 
            rename(value = sim_births_seasonal) %>% 
            mutate(variable  = "Simulated births",
                   group = "B"),
          seas_trend %>% 
            filter(model == "C") %>% 
            select(month, births_seasonal)  %>% 
            rename(value = births_seasonal) %>% 
            mutate(variable  = "Actual births",
                   group = "B")
        ) %>% 
        mutate(
          variable = variable %>% 
            factor(., levels = c("Sex", "Fertility","Simulated births", "Actual births"))
        ) %>% 
        rename(Month = month)
      
      ggplot(amplitudes_df,
             aes(x = Month, y = value, col = variable)) +
        geom_line() +
        geom_point() +
        facet_grid(group ~ ., scale = "free") +
        ggtitle(loc %>%  str_replace(., " - ","\n")) +
        scale_color_manual("",values = c(model_colors, "black")) +
        scale_y_continuous(breaks = 0, minor_breaks = 10) +
        scale_x_continuous(breaks = seq(0,12,by = 3), minor_breaks = 1:12) +
        theme(strip.text.y = element_blank()) +
        ylab("Seasonal trends")
      
    }
  )

suppl_fig_4 = ggarrange(
  plotlist = suppl_fig_4_list,
  ncol = 6, nrow = 1, 
  common.legend = TRUE, legend = "bottom",
  labels = "auto",
  align = "hv"
)


```




### Assembling figure panels


```{r fig3, fig.height=5, fig.width=8}

fig_3 = 
  ggarrange(
    ggarrange(g_models, g_st, nrow = 1, widths = c(3,5.5), labels = "auto"),
    ggarrange(g_b, g_F_seas, ncol = 2, nrow = 1, widths = c(10,3), labels = c("c","d")),
    nrow = 2,
    ncol = 1,
    heights = c(1,2)
  )

```




```{r 10-suppl-fig-5}

suppl_fig_5 = 
  ggarrange(
    g_F + theme(plot.title = element_blank(), legend.key.height = unit(30, "pt")),
    g_fert,
    g_fert_solar,
    nrow = 1, ncol = 3, 
    widths = c(3,2,2),
    labels = "auto"
  )

```




## Saving figures and suppl. figures as pdf and png files

```{r 10-saving-figures, cache = FALSE}

Figures_path = "../Figures Tables Media/Figures/"
scale = 2

# Figure 1

ggsave(plot = fig_1, filename = str_c(Figures_path, "F1.pdf"), 
       width = 17.5, height = 12, units = "cm", scale = scale)

ggsave(plot = fig_1, filename = str_c(Figures_path, "F1.png"), 
       width = 17.5, height = 12, units = "cm", scale = scale)

# Supplementary Figure 1

ggsave(plot = suppl_fig_1, filename = str_c(Figures_path, "F1S.pdf"), 
       width = 17.5, height = 15, units = "cm", scale = scale)

ggsave(plot = suppl_fig_1, filename = str_c(Figures_path, "F1S.png"), 
       width = 17.5, height = 15, units = "cm", scale = scale)

# Figure 2

ggsave(plot = fig_2, filename = str_c(Figures_path, "F2.pdf"), 
       width = 17.5, height = 10, units = "cm", scale = scale)

ggsave(plot = fig_2, filename = str_c(Figures_path, "F2.png"), 
       width = 17.5, height = 10, units = "cm", scale = scale)

# Supplementary Figure 2

ggsave(plot = suppl_fig_2, filename = str_c(Figures_path, "F2S.pdf"), 
       width = 17.5, height = 14, units = "cm", scale = scale)

ggsave(plot = suppl_fig_2, filename = str_c(Figures_path, "F2S.png"), 
       width = 17.5, height = 14, units = "cm", scale = scale)


# Figure 3

ggsave(plot = fig_3, filename = str_c(Figures_path, "F3.pdf"), 
       width = 17.5, height = 12, units = "cm", scale = scale)

ggsave(plot = fig_3, filename = str_c(Figures_path, "F3.png"), 
       width = 17.5, height = 12, units = "cm", scale = scale)


# Supplementary Figure 3

ggsave(plot = suppl_fig_3, filename = str_c(Figures_path, "F3S.pdf"), 
       width = 17.5, height = 14, units = "cm", scale = scale)

ggsave(plot = suppl_fig_3, filename = str_c(Figures_path, "F3S.png"), 
       width = 17.5, height = 14, units = "cm", scale = scale)


# Supplementary Figure 4

ggsave(plot = suppl_fig_4, filename = str_c(Figures_path, "F4S.pdf"), 
       width = 17.5, height = 6, units = "cm", scale = scale)

ggsave(plot = suppl_fig_4, filename = str_c(Figures_path, "F4S.png"), 
       width = 17.5, height = 6, units = "cm", scale = scale)


# Supplementary Figure 5

ggsave(plot = suppl_fig_5, filename = str_c(Figures_path, "F5S.pdf"), 
       width = 17.5, height = 6, units = "cm", scale = scale)

ggsave(plot = suppl_fig_5, filename = str_c(Figures_path, "F5S.png"), 
       width = 17.5, height = 6, units = "cm", scale = scale)

```







